Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-07-26 tex/Main Text/manuscript.tex
7月26给老师看

\subsection*{Drivers of regime shifts}
Two regime shifts had distinct main drivers.
% 第一个 regime shift 包含着

@@

\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/framework}
	\caption{Placeholder image of a frog with a long example legend to show justification setting.}
	\label{fig:framework}
\end{figure*}

>>>>

\subsection*{Drivers of regime shifts}
Based on our model, two regime shifts had distinct main drivers.
% 第一个 regime shift 主要是经济总量提升导致资源耗竭的加速。
%经济总量对用水量预测的能力，经济总量对水资源压力的预测能力。
%经济总量+水库修建对水量、水资源压力的预测
% 第二次 regime shift 发生了用水关系的变化

@@

\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/framework}
	\caption{Transition framework of the water utilization regime.}
	\label{fig:framework}
\end{figure*}
